Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-12 paper/section_4_datasets.tex
Split paper into multiple files

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{multirow} % creates cells that span multiple rows in a table
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm} % bold fonts for math symbols
\usepackage{booktabs}
\usepackage[export]{adjustbox} % adds a frame around figures
\usepackage{IEEEtrantools} % IEEEeqnarray math equation environment
\usepackage{multirow} % merge multiple rows
\usepackage{tabularx} % for 'tabularx' environment
\usepackage{caption} % controls spacing between caption and table

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}

%%%%%%%%% TITLE - suggestions and candidates
\title{Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names}
\title{Transforming Entities for News Image Captions}

\author{Alasdair Tran, Alexander P. Matthews, Lexing Xie\\
Australian National University\\
{\tt\small \{alasdair.tran,alex.matthews,lexing.xie\}@anu.edu.au}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   We propose an end-to-end model to generate image captions in news articles.
   By combining the transformer architecture, byte-pair encoding, and
   pretrained embeddings from three different modalities (RoBERTa for text,
   ResNet-152 for images, and FaceNet for faces), our system is able to
   describe an image with specific named entities mentioned in the article. Our
   model achieves a CIDEr score of 54 on the GoodNews dataset, significantly
   outperforming the previous state-of-art CIDEr of 13. We also introduce the
   NYTimes800k dataset, the largest news image captioning dataset to date.
   NYTimes800k is an extended version of GoodNews with higher-quality articles and
   metadata that allow us to study the importance of the image location within
   the text. On NYTimes800k, we achieve a CIDEr of 55. Pretrained models and
   source code are available from
   \href{https://github.com}{https://github.com/anonymized-link}.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

Most existing captioning systems can only generate a generic description of an
image \cite{Donahue2015LongTR, Vinyals2015ShowAT, Fang2015FromCT,
Karpathy2015DeepVA, Rennie2017SelfCriticalST, Lu2017KnowingWT,
Anderson2017BottomUpAT, Cornia2019ShowCT}, mainly because these architectures
cannot handle an open vocabulary and early captioning datasets such as MS COCO
\cite{Lin2014MicrosoftCC, Chen2015MicrosoftCC} and Flickr30k
\cite{Young2014FromID} were annotated using only visual cues present in the
image. More recently, datasets such as TIME \cite{Tariq2017ACE}, BreakingNews
\cite{Ramisa2016BreakingNewsAA}, and GoodNews \cite{Biten2019GoodNews} include
real-life captions written by professional journalists. However, existing
models that are trained on these news datasets still need to rely on either
extractive methods or templates to insert named entities.

This motivates us to ask whether it is possible to design a fully end-to-end
model for news image captioning. The model would need to 1) attend to
contextual cues from different modalities and 2) generate captions that contain
specific information including rare proper names that have not been seen in the
training data. To answer this, we look at the recent development in
sequence-to-sequence architectures and language representation learning.

The most successful family of models in the field of natural language
processing (NLP) are the transformer networks, which consist of layers of
self-attention and feed-forward connections stacked on top of each other
\cite{Vaswani2017AttentionIA}. Transformers have consistently been shown to
outperform RNN architectures in language modeling \cite{Radford2019LanguageMA},
story generation \cite{Fan2018HierarchicalNS}, summarization
\cite{Subramanian2019OnEA}, and machine translation \cite{Bojar2018Findings}.
There are theoretical justifications that transformers could be universal
approximations of sequence-to-sequence functions \cite{Anonymous2020AreTU}.

Furthermore, transformers have led to the rise of unsupervised language
representation learning such as BERT \cite{Devlin2019BERT}, XLM
\cite{Lample2019CrosslingualLM}, XLNet \cite{Yang2019XLNetGA}, RoBERTa
\cite{Liu2019RoBERTaAR}, and ALBERT \cite{Lan2019ALBERT}. The contextual word
embeddings provided by these methods have helped establish new state-of-the-art
results on many natural language understanding benchmarks including GLUE
\cite{Wang2019GLUE}, SuperGLUE \cite{Wang2019SuperGLUEAS}, and SQuAD
\cite{Rajpurkar2016SQuAD, Rajpurkar2018KnowWY}, even surpassing the human
baselines in many cases.

\begin{figure}[t]
   \begin{center}
      \includegraphics[width=0.99\linewidth, frame]{figures/figure_1.pdf}
   \end{center}
      \caption{Our transformer model attends to embeddings from three different
      domains (image patches, faces, and article text). Using byte-pair
      encoding, the model can then directly produce a caption containing
      specific named entities without the use of templates.}
   \label{fig:long}
   \label{fig:onecol}
\end{figure}

In parallel to the development of these pre-training methods, many novel
techniques have been proposed to improve training convergence and handle more
diverse data inputs. The most significant contribution is the use of byte-pair
encoding (BPE) \cite{Sennrich2015NeuralMT} to represent a rare word as a
sequence of subword units, thus giving models the ability to handle an open
vocabulary.

The goal of this paper is to make use of these recent developments, along with
their bags of tricks, to carefully design a captioning system most appropriate
for news images. Our main contributions are thus threefold:

\begin{enumerate}
   \item We introduce NYTimes800k, the largest news image captioning dataset to
   date, containing 446K articles and 794K images with captions from The New
   York Times spanning 14 years. NYTimes800k is built upon the GoodNews dataset,
   but we write a custom parser to collect higher-quality articles and metadata
   such as the location of an image within the page.

   \item We build a captioning model that combines the power of transformers,
   byte-pair encoding, and attention over three different modalities (text,
   images, and faces). We show that our model achieves state-of-the-art results
   with a significant margin over previous methods, and in particular, it can
   generate names not seen during training without the use of templates.

   \item We provide a detailed model analysis, deconstructing the most
   important modeling components and quantifying the incremental contribution
   that each of them makes not only to the usual metrics such as BLEU, ROUGE,
   METEOR, and CIDEr; but also to other linguistic measures like readability
   scores, caption length, and recall of rare names.
\end{enumerate}

\section{Related Works}

Early image captioning systems mainly used an RNN architecture with a closed
vocabulary \cite{Karpathy2015DeepVA, Donahue2015LongTR, Vinyals2015ShowAT}.
Attention over image patches was later introduced in ``Show, Attend and Tell"
\cite{Xu2015ShowAA}, in which the attention weights are obtained by feeding the
image embeddings and the previous hidden state of the RNN through a multilayer
perception. Later improvements include giving the model the option to not
attend to any image region \cite{Lu2017KnowingWT}, using reinforcement learning
to directly optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST,
Gao2019DeliberateAN}, and using a bottom-up approach to propose a region to
attend to \cite{Anderson2017BottomUpAT}. All of these systems can only generate
generic captions with a limited vocabulary.

A more challenging task is to produce captions for news images, in which we
need to be able to generate entity names. Early non-neural approaches include
extractive methods that use n-gram models to combine existing phrases
\cite{Feng2013AutomaticCG} or simply retrieving the most representative
sentence \cite{Tariq2017ACE} in the article. Ramisa \etal
\cite{Ramisa2016BreakingNewsAA} concatenated the word2vec representation of the
article and and the VGG19 representation of the image, and feed them as inputs
to an LSTM generator. However the generator still cannot produce names not
seen in training.

To overcome the limitation of a fixed-size vocabulary, template-based methods
have been used to insert named entities. This involves first generating a
template sentence with placeholders, e.g. ``PERSON speaks at BUILDING in
DATE.'' Afterwards, a selection algorithm is used to pick the best candidate
for each placeholder. Lu \etal \cite{Lu2018EntityAI} built a knowledge graph
for each combination of entities and select the most likely combination.
Meanwhile Biten \etal~\cite{Biten2019GoodNews}, whose GoodNews dataset we will
benchmark against, picked the sentence with the highest cosine similarity with
the template and then found the first entity that matches the type of each
placeholder for insertion. Our proposed model differs from
\cite{Lu2018EntityAI} and \cite{Biten2019GoodNews} in that we are able to
generate a caption with named entities directly without using any intermediate
template.

Transformers are still scarcely used in image captioning. They have been shown
to yield competitive results in generating generic MS COCO captions
\cite{Zhu2018CaptioningTW, Li2019Boosted}. Zhao \etal
\cite{Zhao2019InformativeIC} have gone further and trained transformers to
produce named entities in the Conceptual Captions dataset
\cite{Sharma2018ConceptualCA}. However Conceptual Captions have no additional
context apart from the image itself, and the authors used web-entity labels,
extracted using Google Cloud Vision API, as inputs to the model. In our work,
we are more ambitious in that we do not explicitly give the model a list of
entities that should appear in the caption. Instead the model has to determine
on its own which entities to generate by scanning through and attending to the
article.

BPE offers an elegant solution to handling an open vocabulary. To date the only
image captioning work that uses BPE is \cite{Sharma2018ConceptualCA}, but in
their data preprocessing step, they explicitly removed rare named entities from
the captions. We attempt to fill this gap and in particular examine how much
better BPE can generate rare names compared to template-based methods.

In addition to attending to image patches, some captioning models also attend
to object regions \cite{Wang2019Hierarchical} and visual concepts
\cite{You2016ImageCW,Li2019Boosted,Wang2019Hierarchical}, both of which are
derived from the image itself. When attending to more than one modality, there
are various strategies on how to combine embeddings such as addition,
concatenation, and using multivariate residual modules (MRMs)
\cite{Kim2016MultimodalRL}. In our models, we use a simple concatenation since
more complex strategies such as MRMs have shown to yield only minor improvement
\cite{Wang2019Hierarchical}.

@@

\begin{figure*}[t]
   \begin{center}
   \fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
   \end{center}
      \caption{Overall architecture of the model.}
   \label{fig:short}
\end{figure*}

@@

\begin{table*}[t]
   \caption {BLEU, ROUGE, METEOR, and CIDEr metrics on GoodNews and
             NYTimes800k.}

	\label{tab:results}
	\centering
	\begin{tabularx}{\textwidth}{llXXXXXXX}
		\toprule
		 & & BLEU-1  & BLEU-2 & BLEU-3 & BLEU-4 & ROUGE & METEOR & CIDEr\\
      \midrule
      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}}
      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 9.04 & 3.66 & 1.71 & 0.89 & 12.2 & 4.37 & 13.1 \\
      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews} & 8.10 & 3.33 & 1.60 & 0.85 & 11.9 & 4.23 & 12.8 \\
      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews} & 8.44 & 3.42 & 1.62 & 0.87 & 12.2 & 4.30 & 13.1 \\
      % Biten (Avg + AttIns) \cite{Biten2019GoodNews} & 8.68 & 3.47 & 1.58 & 0.82 & 12.1 & 4.23 & 12.6 \\
      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews} & 7.74 & 3.15 & 1.45 & 0.75 & 11.9 & 4.10 & 12.5 \\
      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 8.10 & 3.26 & 1.48 & 0.76 & 12.2 & 4.17 & 12.7 \\
      \cmidrule{2-9}
      % & GloVe + LSTM & 13.6 & 6.19 & 3.13 & 1.81 & 13.5 & 5.26 & 11.9 \\
      % & GloVe + Transformer & 17.2 & 8.68 & 4.81 & 2.91 & 16.4 & 7.13 & 22.2 \\
      % & RoBERTa + LSTM & 18.7  & 10.3 & 6.09 & 3.89  & 18.0  & 8.19 & 34.8  \\
      & GloVe + LSTM &  &  &  &  &  &  &  \\
      & GloVe + Transformer &  &  &  &  &  &  &  \\
      & RoBERTa + LSTM &  &  &  &  &  &  &   \\
      & RoBERTa + Transformer & 22.2 & 13.4 & 8.68 & 5.99 & 21.2 & 10.1 & 52.9 \\ % Final
      & \quad + faces & 22.4 & 13.6 & 8.84 & 6.10 & 21.3 & 10.3 & 53.9 \\ % Final
      & \quad\quad + copying \\
      \midrule
      \multirow{6}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
      & GloVe + LSTM & 13.4 & 6.00 & 3.05 & 1.76 & 13.2 & 5.36 & 12.2 \\ % Final
      & GloVe + Transformer & 17.0 & 8.42 & 4.63 & 2.79 & 16.1 & 6.99 & 20.6 \\ % Final
      & RoBERTa + LSTM & 18.0 & 9.88 & 5.97 & 3.91 & 17.1 & 7.96 & 30.8 \\ % Final
      & RoBERTa + Transformer & 20.7 & 12.4 & 8.14 & 5.73 & 19.8 & 9.54 & 44.1 \\ % Final
      & \quad + location-aware & 21.7 & 13.3 & 8.84 & 6.25 & 21.3 & 10.3 & 52.4 \\ % Final
      & \quad\quad + faces & 22.1 & 13.6 & 9.05 & 6.41 & 21.7 & 10.4 & 54.7 \\ % Final
      & \quad\quad\quad + copying \\
      \bottomrule
	\end{tabularx}
\end{table*}

\section{Model Architecture}

\subsection{Model Inputs}

Our proposed model takes three inputs: the image, the faces, and article text.
Each of these inputs first goes through an encoder to give us a vector
representation.

\subsubsection{Image Embedding}

For the image, we feed it through a pretrained ResNet-152 model
\cite{He2016ResNet} and use the output of the final block, just before the
pooling layer, as the image embedding $\bm{x}_I \in \mathbb{R}^{2048 \times 7
\times 7}$. The embedding forms a 7 by 7 block, allowing the transformer to
attend to 49 different patches in the image.

\subsubsection{Article Embedding}

For the article, we use RoBERTa \cite{Liu2019RoBERTaAR} to encode the text.
RoBERTa is a language representation model that provides pretrained contextual
embeddings for text. It consists of 24 layers of bidirectional transformer
blocks. It is a more carefully trained BERT \cite{Devlin2019BERT} model.

Unlike GloVe \cite{Pennington2014Glove} and word2vec
\cite{Mikolov2013DistributedRO} embeddings, where each word has exactly one
representation, the bidirectionality and the attention mechanism in the
transformer allow a word to have different vector representations depending on
the surrounding context.

The largest GloVe model has a vocabulary size of 1.2 million. Although this is
large, many rare names will still get mapped to the unknown token. In contrast,
RoBERTa uses BPE \cite{Sennrich2015NeuralMT,Radford2019LanguageMA} which can
encode any word that can be written in Unicode characters.

Given an input of length $S$, the pretrained RoBERTa encoder will return 25
sequences of embeddings, $\bm{h}_i \in \mathbb{R}^{2048 \times S}$ for $i \in
\{0,1, 2,...,24\}$. This includes the initial uncontextualized embeddings and
the output of each of the 24 layers. Inspired by Tenney \etal
\cite{Tenney2019BertRT}, who showed that different layers in BERT represent
different steps in the traditional NLP pipeline, we take a weighted sum
across all layers to obtain the article embedding:
\begin{IEEEeqnarray*}{lCl}
   \bm{x}_T &=& \sum_{i=0}^{24} w_i \bm{h}_i
\end{IEEEeqnarray*}
where $\bm{x}_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
and $w_i$ are learnable weights.

One limitation of RoBERTa is that the maximum length of the input sequence is
512. For GoodNews, we simply encode the first 512 tokens of the article. For
NYTimes800k, since we have the image position, we concatenate the title, the
first paragraph, and as many paragraphs above and below the image as we can
fit, until we reach the 512 token limit. Note that since we are using BPE, a
token can be part of a word. On average, we can only encode ...... words of
the article.

\subsubsection{Face Embedding}

To embed the faces, we first use MTCNN \cite{Zhang2016JointFD} to detect the
face bounding boxes. We then select the top $M$ faces and feed them through a
FaceNet model \cite{Schroff2015FaceNetAU}, pretrained on the VGGFace2 dataset
\cite{Cao2017VGGFace2AD}, to obtain a face embedding $\bm{x}_F \in
\mathbb{R}^{512 \times M}$ where $M$ is the number of faces.

\subsection{Decoder}

\subsubsection{Dynamic Convolutions}

Our decoder is a transformer architecture with dynamic convolutions
\cite{Wu2018PayLA} containing four layers with kernel sizes 3, 7, 15 and 31. We
found that using dynamic convolutions allows the training to converge faster
than using the current state-of-the-art GPT-2 architecture
\cite{Radford2019LanguageMA}.

In the standard self-attention module, the input embedding $\bm{x} \in
\mathbb{R}^{1024}$ is first projected linearly into a query, key, and value
$\bm{q}, \bm{k}, \bm{v} \in \mathbb{R}^{1024}$. Then the attention is the
weighted sum of the values, where the weights are obtained from the dot product
between the key and value:
\begin{IEEEeqnarray*}{lCl}
   \text{Attention}(\bm{x}) &=&
   \text{softmax}\left( \dfrac{\bm{q} \bm{k}^T}{\sqrt{d_K}} \right) \bm{v}
\end{IEEEeqnarray*}

\begin{table*}[t]
   \caption {Named entity, personal name, and rare proper noun recall \&
             precision on GoodNews and NYTimes800k.}
	\label{tab:names}
	\centering
	\begin{tabularx}{\textwidth}{llXXXXXX}
		\toprule
      &  & \multicolumn{2}{c}{Named entities} & \multicolumn{2}{c}{Personal names} & \multicolumn{2}{c}{Rare proper nouns} \\
      &  & Recall  & Precision & Recall  & Precision & Recall  & Precision \\
      \midrule
      \multirow{8}{*}{\rotatebox[origin=c]{90}{GoodNews}}
      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews} & 6.06\% & 8.23\% & 6.55\% & 9.38\% & -- & -- \\
      & Biten (TBB + AttIns) \cite{Biten2019GoodNews} & 5.64\% & 8.87\% & 6.98\% & 11.9\% & -- & -- \\
      \cmidrule{2-8}
      & GloVe + LSTM & & &  &  & -- & --  \\
      & GloVe + Transformer & & &  &  & -- & -- \\
      & RoBERTa + LSTM & &  &  &  & -- & -- \\
      & RoBERTa + Transformer & 18.4\% & 21.6\% & 22.4\% & 28.1\% & -- & -- \\
      & \quad + faces & 18.7\% & 22.1\% & 23.2\% & 29.2\% & -- & -- \\
      & \quad\quad + copying \\
      \midrule
      \multirow{7}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
      & GloVe + LSTM & 7.26\% & 10.2\% & 5.69\% & 8.61\% & 0\% & 0\%  \\
      & GloVe + Transformer & 10.9\% & 13.4\% & 9.50\% & 13.5\% & 0\% & 0\%  \\
      & RoBERTa + LSTM & 15.0\% & 17.1\% & 18.1\% & 22.6\% & 15.1\% & 15.2\% \\
      & RoBERTa + Transformer & 19.5\% & 21.0\% & 25.5\% & 30.3\% & 22.6\% & 29.1\% \\
      & \quad + location-aware & 21.9\% & 24.1\% & 30.2\% & 35.5\% & 26.2\% & 32.5\% \\
      & \quad\quad + faces & 22.3\% & 24.5\% & 31.3\% & 37.1\% & 26.6\% & 33.6\% \\
      & \quad\quad\quad + copying \\
		\bottomrule
	\end{tabularx}
\end{table*}

\subsubsection{Adaptive Softmax}

The BPE vocabulary size is 50265. To make training more efficient, we use adaptive softmax
\cite{Grave2016EfficientSA} and divide the vocabulary into three clusters: 5K,
15K, and 25K. We tie the adaptive weights and we share the decoder input and
output embeddings. We use sinusoidal positional encoding
\cite{Vaswani2017AttentionIA} to represent the position of each token.

\subsubsection{Encoder Attention}

For each generation step, we use the Scalar-Dot-Product attention
\cite{Vaswani2017AttentionIA} to attend to the image, article, and faces. All
of the three attended representations are then concatenated and fed as input to
the self-attention layer.

\section{Experiments}

\subsection{Training Details}

In all experiments, we use Adam \cite{Kingma2015Adam} with the weight decay fix
\cite{Loshchilov2018DecoupledWD} to optimize the models. We use the following
parameters: $\beta_1 = 0.9, \beta_2 = 0.98, \epsilon = 10^{-6}$, and a weight
decay of $10^{-5}$. We clip the gradient norm at 0.1. All models see the same
number of training examples, which is 6.6 million. This is equivalent to 16
epochs through GoodNews and 9 epochs through NYTimes800k. We warm up the
learning rate in the first 5\% of the training steps to $10^{-4}$, and
afterward decays it linearly. Training the full model takes 5 days on one Titan
V GPU.

As shown in Table \ref{tab:models}, all of our baselines are designed to have
roughly the same number of trainable parameters. This allows us to attribute
improvement to the individual model components rather than to simply having a
bigger model.

The training pipeline is written in PyTorch \cite{Paszke2017Automatic} using
the AllenNLP framework \cite{Gardner2017AllenNLP}. The RoBERTa model and
dynamic convolution code are adapted from fairseq \cite{Ott2019Fairseq}.

\begin{table}[t]
	\caption {Model complexity}
	\label{tab:models}
	\centering
	\begin{tabularx}{\linewidth}{Xc}
		\toprule
        & No. of Parameters \\
      \midrule
      GloVe + LSTM & 157M \\
      GloVe + Transformer & 148M \\
      RoBERTa + LSTM & 159M \\
      RoBERTa + Transformer & 154M \\
      \quad + faces & 171M \\
      \quad\quad + copying & 207M \\
		\bottomrule
	\end{tabularx}
\end{table}

\subsection{Results}

Table \ref{tab:results} shows the BLEU \cite{Papineni2002Bleu}, ROUGE
\cite{Lin2004ROUGE}, METEOR \cite{Denkowski2014Meteor}, and CIDEr
\cite{Vedantam2015CIDEr} metrics on GoodNews and NYTimes800k. We show two best
results from the previous state-of-the-art \cite{Biten2019GoodNews}. Note that
the numbers reported here are slightly different from the original paper since
we had to remove a few samples from the test set where the image is no longer
available. \cite{Biten2019GoodNews} also did some post-processing on the
ground-truth captions such as removing contractions and non-ASCII characters,
both of which we did not do. Despite these differences, the final metrics
are the same if rounded to the nearest whole number.

There is a strong correlation between of all these metrics, and in general, we
mainly look at CIDEr since it uses Term Frequency Inverse Document Frequency
(TF-IDF) to put more importance on less common words such as entity names.
Table \ref{tab:names} shows the recall and precision of the named entities,
personal names, and rare proper nouns.

We can make the following observations:

\begin{itemize}
   \item Our baseline LSTM model with GloVe embeddings yields competitive
   results to previous the state-of-the-art \cite{Biten2019GoodNews}. This
   means that BPE offers a viable alternative to template-based methods.

   \item Models with GloVe embeddings are unable to generate rare proper nouns.
   This is expected since GloVe has a fixed vocabulary and if there is a
   unknown word in the article, the encoder will simply skip it.

   \item Switching from an LSTM to a transformer architecture improves the
   CIDEr score on NYTimes800k by 8 points, from 12 to 20. If we then use the
   contextualize RoBERTa embeddings instead of GloVe, CIDEr more than doubles
   to 44.

   \item Adding attention over the faces improves both the recall and precision
   of personal names. It has no significant effect on other entity types (see
   the supplementary materials for a detailed breakdown).
\end{itemize}

\begin{table}[t]
   \caption {Linguistic measures on the generated captions: caption length (CL),
             type-token ratio (TTR), and Flesch readability ease (FRE).}
	\label{tab:caption}
	\centering
	\begin{tabularx}{\linewidth}{llXXX}
		\toprule
       &  &  CL  & TTR & FRE \\
      \midrule
      \multirow{9}{*}{\rotatebox[origin=c]{90}{GoodNews}}
      & Ground Truths & 18.1 & 94.9 & 65.4 \\
      \cmidrule{2-5}
      & Biten (Avg + CtxIns) \cite{Biten2019GoodNews}  & 9.9 & 92.2 & 78.3 \\
      % Biten (Wavg + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
      % Biten (TBB + CtxIns) \cite{Biten2019GoodNews}  & 9.2 &  \\
      % Biten (Avg + AttIns) \cite{Biten2019GoodNews}  & 9.7 &  \\
      % Biten (Wavg + AttIns) \cite{Biten2019GoodNews}  & 9.0 &  \\
      & Biten (TBB + AttIns) \cite{Biten2019GoodNews}  & 9.1 & 90.7 & 77.6 \\
      \cmidrule{2-5}
      & GloVe + LSTM &  &  \\
      & GloVe + Transformer &  &  \\
      & RoBERTa + LSTM &  &   \\
      & RoBERTa + Transformer & 15.5 & 91.0 & 72.0 \\
      & \quad + faces & 15.5 & 90.7 & 71.9 \\
      & \quad\quad + copying \\
      \midrule
      \multirow{8}{*}{\rotatebox[origin=c]{90}{NYTimes800k}}
      & Ground Truths & 18.4 & 94.6 & 63.9 \\
      & GloVe + LSTM  & 13.8 & 89.0 & 77.8 \\
      & GloVe + Transformer  & 15.1 & 88.6 & 73.8 \\
      & RoBERTa + LSTM  & 14.9 & 90.2 & 72.6 \\
      & RoBERTa + Transformer  & 15.3 & 91.5 & 70.4 \\
      & \quad + location-aware & 15.1 & 91.7 & 70.4  \\
      & \quad\quad + faces & 15.2 & 91.6 & 70.5 \\
      & \quad\quad\quad + copying \\
		\bottomrule
	\end{tabularx}
\end{table}

Table \ref{tab:caption} look at the quality of the generated captions. We look
at three metrics: caption length, type-token ratio (TTR), and Flesch reading
ease. TTR is the ratio of the number of unique words to the total number of
words in a caption. The Flesch reading ease takes into account the number of
words and syllables and produces a score between 0 and 100, where higher means
being easier to read.

From these metrics, we see that our generated captions are in general still
shorter than real-life captions, have lower lexical diversity (lower TTR)
and still use simpler language (higher Flesch reading ease).

\section{Conclusion}

{\small
\bibliographystyle{ieee_fullname}
\bibliography{paper}
}

\end{document}

>>>>

% !TEX root = main.tex

@@

@@
